---
title: "Assignment8"
author: "Sushil54_Sharad_43"
date: "9/12/2019"
output: html_document
---
1.	Import the dataset (male_names.csv) and find the frequency of name "GRANT" using visualization.
Make use of all possible arguments in the function you use (For example: xlab, ylab, main, type etc)
```{r GraphicalAnalysis}
w<-read.csv("male_names.csv")
names(w)
male_name<-data.frame(w)
male_name
r<-which(male_name$Name=="GRANT")
r
year=male_name[r,1]
year
freq=male_name[r,3]
freq
boxplot(year,freq,xlab="YEAR",ylab = "FREQUENCY")
plot(year,freq,xlab="YEAR",ylab = "FREQUENCY")
barplot(year,freq,xlab="YEAR",ylab = "FREQUENCY")
```
2.	Import student dataset (StudentsMarks.csv), by graphical analysis find out which student has got zero mark in one of the subjects.
```{r}
q<-read.csv("StudentsMarks.csv")
q

names(q)
r<-which(q$Marks==0)
r
zero=q[r,1]
nostu=q[r,2]
plot(nostu,zero,xlab="ZERO_MARKS",ylab = "NO.OF STUDENTS")
```
3.	Import Environment data. Make a well labeled graph to see a relation between the variables.
Explain your reasoning 
```{r}
q<-read.csv("Environment.csv")
q
names(q)
nocs=q[,1]
nocr=q[,2]
plot(nocs,nocr,xlab="No. of cans sold",ylab = "No. of cans Recycled")
```
4.	Import Climate data and visualize the parameters from col4 to col8 and explain your reasoning
```{r}
w<-read.table("weather.txt",header = T)
w
d<-data.frame(w)
d
f<-d[,4:8]
f
plot(d[,4:8])

```
