---
title: "Assignment7"
author: "Sushil54_Sharad_43"
date: "9/12/2019"
output: html_document
---
1. Create a R function to calculate the standard deviation.
Function should take single integer vector as an argument.
Give the name of function as StDev()
```{r}
StDev<-function(z)
{
 table<-sd(z)
 res<-paste(table,sep="")
 return(res)
}
sd(c(25,34,12,67,54))
```
2. Create a R function to calculate the standard deviation.
Function should take integer vector as first argument and for second argument use "FUN" and assign sd() function to it.
Give the name of function as StDev1()
```{r}
FUN<-StDev
StDev1<-function(z,FUN)
{
 table<-sd(z,FUN())
 res<-paste(table,sep="")
 return(res)
}
sd(c(25,34,12,67,54))
```
3. Create a function to calculate the running average of integer vector.
Give the function name as RunAvg()
```{r}
RunAvg<-function(s)
{
table<-mean(s)
res<-paste(table,sep="")
return(res)
}
RunAvg(c(23,34,45,323212,45))
```
4. The below given code takes n number of integers as arguments and calculates the sum of it 

```{r}
Sumall <- function(...)
{ arguments <- list(...) 
result=paste(arguments) 
sum(as.integer(result))
}
Sumall(45,98,104,8677)
```
5.The below given code n number of objects as arguments.

```{r}
s<-34
d<-c(34,90,78,56)
f<-34
Obj <- function(...) 
{
arguments <- c(...) 
result=paste(arguments) 
return(as.data.frame(result))
}
Obj(s,d,f)
```

