---
title: "Assignment66"
author: "Sushil54_Sharad_43"
date: "9/13/2019"
output: html_document
---

---
title: "Assignment6"
author: "Sushil54_Sharad43"
date: "9/12/2019"
output: html_document
---
```{r }
library(tidyr)
mydata=read.csv(file="Datasets/sampledata.csv")
mydata
mydata1=gather(mydata ,"Year","Values",3:16)
mydata1
mydata2=spread(mydata1,"Year","Values")
mydata2
```
2.Import cases dataset and arrange all the values of year's (2011,2012,2013) in a new column (we call it as key) and its corresponding values. (refer Presentation)
```{r}
mycases=read.table(file="Datasets/cases.txt")
colnames(mycases)<-c("country","2011","2012","2013")
mycases1=mycases[2:length(mycases$country),]
mydata3=gather(mycases1,"key","value",2:4)
mydata3
```
3. Import the pollution data and re-arrange the values from the second and third column. (refer Presentation)
4.
```{r}
library(dplyr)
mypoll=read.table(file = "Datasets/pollution.txt",sep="\t")
colnames(mypoll)<-c("city","size","amount")
mypoll1<-mypoll[2:length(mypoll$city),]
mypoll1
a1=arrange(mypoll1,size,amount)
a1
```
4. Consider the TB dataset. Dataset name is "TB_burden_countries_2016-02-27" (dataset is shared) and metadata of this dataset is also shared (TB_data_dictionary_2016-02-27). You don't have to import metadata file.
```{r}
library(dplyr)
myfile1=read.csv(file = "Datasets/TB_burden_countries_2016-02-27.csv",header=T)
myfile1
```
ii. Find the dimensions of the data, rownames, columnanes of the dataset and note the observations.
```{r}
dim(myfile1)
head(rownames(myfile1))
colnames(myfile1)
```

iii. Find in which year and in which country, estimated number of incident cases are more? (You can see the exact column name of " estimated number of incident cases " from the metadata file)
```{r}
rowindex<-which(myfile1$e_inc_num==max(myfile1$e_inc_num))

myfile1[rowindex,c(1,6,32)]
```
Import the datasets and try all the functions of dplyr package that are shown in the presentation
```{r}
options(repos=c(CRAN="http://cran.rstudio.com"))
library(dplyr)
library(tidyr)
mydata=read.csv(file = "Datasets/sampledata.csv")

obj51 = select(mydata, Index, State:Y2008)
obj51
obj52=filter(mydata, Index == "A")
obj52
arrange1=arrange(mydata, Index, Y2011)
arrange1
GroupedData = group_by(mydata, Index)
GroupedData
summarise(mydata, Y2015_mean = mean(Y2015), Y2015_median = median(Y2015))
My_mutate = mutate(mydata, change=Y2015/Y2014)
My_mutate
```

